Benchmarking on Rigetti architecture

### 2022-06-21 txt-softwarex/SoftwareX_article_template.tex
add the beginning of sction about example

\newcommand{\eg}{{\emph{e.g.\/}}}
\newcommand{\ie}{{\emph{i.e.\/}}}
\newcommand{\ket}[1]{\ensuremath{|#1\rangle}}
\newcommand{\bra}[1]{\ensuremath{\langle#1|}}
\newcommand{\ketbra}[2]{\ensuremath{\ket{#1}\bra{#2}}}
\newcommand{\proj}[1]{\ensuremath{\ketbra{#1}{#1}}}
\newcommand{\braket}[2]{\ensuremath{\langle{#1}|{#2}\rangle}}
\newcommand{\floor}[1]{\ensuremath{\lfloor #1 \rfloor}}
\newcommand{\complexity}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\new}[1]{ \textcolor{red}{#1} }
\newcommand{\1}{{\rm 1\hspace{-0.9mm}l}}
\newcommand{\Id}{{\rm 1\hspace{-0.9mm}l}}
\newcommand{\connected}{\sim}
\newcommand{\SPAN}{\mathrm{span}}
\newcommand{\Lrm}{\ensuremath{\mathrm{L}}}
\newcommand{\Urm}{\ensuremath{\mathrm{U}}}
\newcommand{\ee}{\ensuremath{\mathrm{e}}}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\ii}{\ensuremath{\mathrm{i}}}
\newcommand{\EE}{\mathcal{E}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\MM}{\mathcal{M}}
\newcommand{\NN}{\mathcal{N}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\TT}{\mathcal{T}}
\newcommand{\PP}{\mathcal{P}}
\renewcommand{\SS}{\mathcal{S}}
\newcommand{\UU}{\mathcal{U}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\DU}{\mathcal{DU}}
\newcommand{\NOT}{\sigma_x}
\newcommand{\idop}[1][\XX]{\ensuremath{\1_{#1}}}
\newcommand{\diaguni}{\ensuremath{\mathcal{DU}}}
%\DeclareMathOperator{\diag}{diag}
%\DeclareMathOperator{\diag}{diag}
\journal{SoftwareX}

@@

Let us now consider linear mappings transforming  square matrices into square 
matrices 
that is \ $\Phi: M_{d_1} \to M_{d_2}$. 
 We define its completely bounded trace
	norm, also known as a diamond norm, as
	\begin{equation}
	\|\Phi\|_\diamond = \max_{\|X\|_1=1} \| \left(\Phi \otimes \1\right) (X) \|_1.
	\end{equation}

@@

In the general case, the diamond norm of a Hermiticity-preserving maps $\Phi$ can be computed using the Semidefinite Program~\cite{watrous2018theory} and state 
primal and dual problem in the following form:

@@

\section{Illustrative Examples}
\subsection{One-qubit measurements}
Let us consider one-qubit von Neumann measurements $\PP_U$ and $\PP_\Id$. In this simplest case,  we consider two von Neumann measurements $\PP_\1$ and $\PP_U$ for $U = H_2 diag(0,\ee^{\ii \phi}) H_2$, where $H_d$--Hadamard matrix of dimension $d$, $0 \le \phi < 2\pi$.    By theoretical results, the expected probability $p_{success}$ of correct distinction between two measurements $\PP_\1$ and $\PP_U$  is given by
\begin{equation}
p_{success} = \frac{1}{2} + \frac{1}{4} ||\PP_U - \PP_\1 ||_\diamond = \frac{1}{2} + \frac{|1-\ee^{\ii \phi}|}{4}
\end{equation}
by the assumption the discriminator is on the form $\ket{\psi} = \frac{1}{\sqrt{2}} ( \ket{00} +  \ket{11} )$. 
(tu wyniki z rigettiego...)

\subsection{Two-qubit measurements}

>>>>

\newcommand{\eg}{{\emph{e.g.\/}}}
\newcommand{\ie}{{\emph{i.e.\/}}}
\newcommand{\ket}[1]{\ensuremath{|#1\rangle}}
\newcommand{\bra}[1]{\ensuremath{\langle#1|}}
\newcommand{\ketbra}[2]{\ensuremath{\ket{#1}\bra{#2}}}
\newcommand{\proj}[1]{\ensuremath{\ketbra{#1}{#1}}}
\newcommand{\braket}[2]{\ensuremath{\langle{#1}|{#2}\rangle}}
\newcommand{\floor}[1]{\ensuremath{\lfloor #1 \rfloor}}
\newcommand{\complexity}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\new}[1]{ \textcolor{red}{#1} }
\newcommand{\1}{{\rm 1\hspace{-0.9mm}l}}
\newcommand{\Id}{{\rm 1\hspace{-0.9mm}l}}
\newcommand{\connected}{\sim}
\newcommand{\SPAN}{\mathrm{span}}
\newcommand{\Lrm}{\ensuremath{\mathrm{L}}}
\newcommand{\Urm}{\ensuremath{\mathrm{U}}}
\newcommand{\ee}{\ensuremath{\mathrm{e}}}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\ii}{\ensuremath{\mathrm{i}}}
\newcommand{\EE}{\mathcal{E}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\MM}{\mathcal{M}}
\newcommand{\NN}{\mathcal{N}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\TT}{\mathcal{T}}
\newcommand{\PP}{\mathcal{P}}
\renewcommand{\SS}{\mathcal{S}}
\newcommand{\UU}{\mathcal{U}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\DU}{\mathcal{DU}}
\newcommand{\NOT}{\sigma_x}
\newcommand{\idop}[1][\XX]{\ensuremath{\1_{#1}}}
\newcommand{\diaguni}{\ensuremath{\mathcal{DU}}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\tr}{\mathrm{tr}}
%\DeclareMathOperator{\diag}{diag}
%\DeclareMathOperator{\diag}{diag}
\journal{SoftwareX}

\newtheorem{theorem}{Theorem}

@@

\subsubsection{Diamond norm}
Let us now consider linear mappings transforming  square matrices into square 
matrices 
that is \ $\Phi: M_{d_1} \to M_{d_2}$. 
 We define its completely bounded trace
norm, also known as a diamond norm, as
\begin{equation}
\|\Phi\|_\diamond = \max_{\|X\|_1=1} \| \left(\Phi \otimes \1\right) (X) \|_1.
\end{equation}

@@

\begin{theorem}
Let $U\in \UU_d$ and let $\PP_U$ and $\PP_\Id$ be two von Neumann 
measurements. 
Let also 
$\diaguni_d$ be the set of diagonal unitary matrices of dimension $d$. Then
\begin{equation}
\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
\Phi_\Id\|_\diamond,
\end{equation}
where $\Phi_U$ is unitary channel.
\end{theorem}

\paragraph{Discrimination of unitary channels}

Before we proceed to presenting our main results, we need to briefly discuss the
problem of discrimination of unitary channels. This can be done without the
usage of entangled input. In order to formulate the condition for perfect
discrimination of unitary channels we introduce the notion of numerical range of
a matrix $A \in M_d$, denoted by $W(A) =\{\bra{x}A\ket{x}: \ket{x} \in 
\mathbb{C}^d, \;
\;\braket{x}{x}=1\}$. The celebrated Hausdorf-T\"oplitz
theorem states that
$W(A)$ is a convex set and therefore $W(A) =\{\tr A \sigma : \sigma \in \Omega_d
\}$. Let us now recall the well-known result for the
distinguishability of unitary channels.
	Let $U \in \UU_d$ and $\Phi_U: \rho \mapsto U \rho U^\dagger$ be a unitary 
	channel. 
	Then 
	\begin{equation}
	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
	\end{equation}
	where $\nu = \min_{x \in W(U^\dagger)} |x|  $.

%\begin{proposition}
 Let $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, $\phi \in [0, 2\pi)$ and	let 
 $\Phi_U$ and $\Phi_\Id$ be two unitary channels. The following equation holds 
	\begin{equation}
	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
	\Phi_\Id\|_\diamond
	\end{equation}
%\end{proposition}

%In the general case, the diamond norm of a Hermiticity-preserving maps $\Phi$ 
%can be computed using the Semidefinite Program~\cite{watrous2018theory} and 
%state 
%primal and dual problem in the following form:

@@

\section{Illustrative Examples}

Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
Assume that the unitary matrix $U$ is of the form 
\begin{equation}
U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
\end{equation}
where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
In this section we will compare theoretical probability of correct 
discrimination between these measurements and the realization on real devices.
The theoretical probability can be calculated using Holevo-Helstrom theorem. 
This probability will be calculated in 
subsection~\ref{sec:example_theoretical_probability}. Later, we will 
discuss the realization of this scheme on real devices in 
subsection~\ref{sec:example_realization}. For such realization, we 
will need the proper input state, (see sec.~\ref{sec:example_discriminator}) 
and final measurement (see sec.~\ref{sec_example_final_measurement}).

\subsection{Theoretical bound}\label{sec:example_theoretical_probability}

\subsection{Realization}\label{sec:example_realization}

\subsubsection{Discriminator}\label{sec:example_discriminator}

\subsubsection{Final measurement}\label{sec_example_final_measurement}

%Let us consider one-qubit von Neumann measurements $\PP_U$ and $\PP_\Id$. In 
%this simplest case,  we consider two von Neumann measurements $\PP_\1$ and 
%$\PP_U$ for $U = H_2 diag(0,\ee^{\ii \phi}) H_2$, where $H_d$--Hadamard matrix 
%of dimension $d$, $0 \le \phi < 2\pi$.    By theoretical results, the expected 
%probability $p_{success}$ of correct distinction between two measurements 
%$\PP_\1$ and $\PP_U$  is given by
%\begin{equation}
%p_{success} = \frac{1}{2} + \frac{1}{4} ||\PP_U - \PP_\1 ||_\diamond = 
%\frac{1}{2} + \frac{|1-\ee^{\ii \phi}|}{4}
%\end{equation}
%by the assumption the discriminator is on the form $\ket{\psi} = 
%\frac{1}{\sqrt{2}} ( \ket{00} +  \ket{11} )$. 
%(tu wyniki z rigettiego...)
